Cover letter for the original IJRR submission

### 2017-09-29 reviews_tro/reviewer_response.tex

\as{We updated Section VIII.B.1) to illustrate the meaning of those terms.}
\qt{We then computed to sensitivity and specificity of the reachability condition.  In this context, the sensitivity refers to the percentage of configurations in $C_{Reach}^0$, effectively belonging to \gls{$C_{Contact}^0$}. If a sampled configuration is in $C_{Reach}^0$, but our method is unable to generate a contact configuration from it, as a result the sensitivity
decreases. The sensitivity thus illustrates the confidence we have that any configuration in $C_{Reach}^0$ will effectively lead to a contact configuration.
Conversely, the specificity refers to the percentage of configurations \textbf{not} in $C_{Reach}^0$, effectively \textbf{not} belonging to \gls{$C_{Contact}^0$}.
If a sampled configuration is \textbf{not} in $C_{Reach}^0$, but our method is able to generate a contact configuration from it, as a result the specificity
decreases. The specificity thus illustrates the confidence we have that all configurations that allow contact creation belong to in $C_{Reach}^0$ (or informally, the confidence that we are not missing too many valid solutions).
We thus look for a compromise between sensitivity and specificity.} \done

\quot{
However, I suggest the paper will be improved if
the presentation focuses more on highlighting (a) what is novel, and
(b)
what take-away messages you have, about why the whole framework is
designed the way it is [within the main text; not hidden in
appendices].}

\as{TODO}\ndone

\quot{
p.6 – this would be a great place to give more ``intuition'' for the heuristics. Hw seems to be used in essentially all foot contact, with $h_{efort}$ for hand/arm contacts, and ALSO $h_{vel}$ not seeming to be used at all.}
\as{Thanks for the suggestion. The text was updated accordingly, and the heuristic $h_{vel}$ was removed since indeed it is not used.} 
\qt{In all our experiments, the heuristic $h$ is implemented as a variation of a manipulability-based heuristic [27]. The manipulability is a real number that quantifies how 
``good'' a configuration is to perform a given task, based on the analysis of the Jacobian matrix. With such heuristics, a configuration can be chosen because it is far from singularities, and thus allows mobility in all directions. On the contrary, it can be chosen because it is particularly efficient to exert a force in a desired direction. In our experiments, the former solution is usually chosen for computing leg contacts, while the latter is used for computing hand contacts. We recall the manipulability measure and its derivatives in Appendix B.}\done

### 2017-09-29 reviews_tro/reviewer_response.tex

\quot{
p.8– somehow, “Table II” doesn’t appear until after “Table IV” – which is a frustrating choice for latex to make. Not sure what you can do to change that, but it would be preferable to have tables (and figures) appear in the correct order.
}

\as{We reorganized the paper such that the Table appear in the right order.}\ndone

\quot{
p.8. Need to define ``discretization step'' more precisely, I think(?)… Min distance? Max distance? Nominal distance? In time? In Distance? In all 6 DOF??
}

\as{The distance considered is the distance travelled along the path, computed as a weighted 6D Euclidian variation along it. We updated the text to clarify this}.
\qt{(Section V.B.1) $j$ depends on a user-defined variable, called the discretization step. It corresponds to the ratio between the length of the path $\mathbf{q}^0(t)$, and the number
of configurations selected along it to create the contact configurations. The length of the path is computed as the weighted 6D Euclidian distance
travelled along the it, with a weight of 0.7 for the translation part, and 0.3
for the orientation part.}

@@

\quot{
p.9 ‘addresses highly constrained environment’ – actually, not very well, correct? This was the “exception” case, for which results were rather poor, right? Also a case where “heuristics” are not so good for getting true (reliable) holds on grasp points, etc.?
}

\as{Thanks for the comment. On this particular point however, we wish to maintain our statement. For scenarios such as the car egress, a success rate of $68 \%$ means that the planner
will fail at some point, but more importantly it means that if we restart the planning a few times with the same problem, there is a reasonable probability that it will find a feasible solution.
In this regard, the car egress scenario is effectively addressed, because we found a solution for it. \\
Furthermore, we believe that this result is to be compared with the current state of the art : we are not aware of any other method who was able
to compute a valid motion from scratch, even in simulation. The closest work to this achievement is the one from Escande et al., but the trajectories were manually interpolated
after the contact plan was designed, and even so we do not have any idea on the success rate of the method. \\
Now regarding the heuristics, we guess that the reviewer is referring to the large number of repositionnings that occured in the contact plan. We believe that this issue
is more related to the kinematic and environmental constraints than the heuristic for the choice of contacts. Developing heuristics that would take into account the environment to limit 
contact repositioning is indeed out of the scope of this work.}

\done

@@

\quot{
The first part of App. B is referred to within this Appendix as “new minor contributions derived from previous work”. These aren’t so novel, perhaps, and what is more useful to the reader is a better intuition for when to use each within the MAIN BODY of the paper, where they are originally described/associated to particular simulations.
}

\as{Agreed. We removed the incriminated text and provided an intuition of the heuristic in the text, as mentioned above.}\done

### 2017-09-29 body/contact.tex
finished r1, added footnote on disctance

\subsection{Contact planning algorithm}
Starting from an initial whole-body configuration, we compute a sequence
of whole-body configurations  $\mathbf{Q}^{\overline{0}}$ along the root path $\mathbf{q}^0(t)$.
We first give an intuition of the algorithm, before providing its complete pseudo-code.
%~ The algorithm can be found in Appendix~\ref{app:contact}. Here we provide an intuition of it.
\subsubsection{Algorithm overview}
First, the root path $\mathbf{q}^0(t)$ is discretized into a sequence of $j$ key configurations:  
\begin{equation*}
	\mathbf{Q}^0 = [\mathbf{q}^0_{0}; \mathbf{q}^0_{i}; ..., \mathbf{q}^0_{j-1}]
\end{equation*} 
where $\mathbf{q}^0_{0}$ and $\mathbf{q}^0_{j-1}$ are the start and goal configurations. %To ensure continuity in the contact transition phases,
Each root configuration of $\mathbf{Q}^0$ is then extended into a whole-body configuration such that:
\begin{itemize} 
\item At most one contact is not maintained (\textit{broken}) between two consecutive configurations.
\item At most one contact is added between two consecutive configurations.
\item Each configuration is in static equilibrium.
\item Each configuration is collision-free.
\end{itemize}

>>>>

\subsection{Contact planning algorithm}
Starting from an initial whole-body configuration, we compute a sequence
of whole-body configurations  $\mathbf{Q}^{\overline{0}}$ along the root path $\mathbf{q}^0(t)$.
We first give an intuition of the algorithm, before providing its complete pseudo-code.
%~ The algorithm can be found in Appendix~\ref{app:contact}. Here we provide an intuition of it.
\subsubsection{Algorithm overview}
First, the root path $\mathbf{q}^0(t)$ is discretized into a sequence of $j$ key configurations:  
\begin{equation*}
	\mathbf{Q}^0 = [\mathbf{q}^0_{0}; \mathbf{q}^0_{i}; ..., \mathbf{q}^0_{j-1}]
\end{equation*}

where $\mathbf{q}^0_{0}$ and $\mathbf{q}^0_{j-1}$ are the start and goal configurations. %To ensure continuity in the contact transition phases,
$j$ depends on a user-defined variable, called the discretization step. It corresponds to the ratio between the length of the path $\mathbf{q}^0(t)$\footnote{The length of the path is computed as the weighted 6D Euclidian distance
travelled along the it, with a weight of $0.7$ for the translation part, and $0.3$ for the orientation part.}, and the number
of configurations selected along it to create the contact configurations. 
Each root configuration of $\mathbf{Q}^0$ is then extended into a whole-body configuration such that:
\begin{itemize} 
\item At most one contact is not maintained (\textit{broken}) between two consecutive configurations.
\item At most one contact is added between two consecutive configurations.
\item Each configuration is in static equilibrium.
\item Each configuration is collision-free.
\end{itemize}
